budget

### 2020-02-25 src/tax2016-2018.Rmd
Update tax2016-2018.Rmd
add output file

Municipalities<-tax.full$Municipalities
pct_2017<-(tax.full$`2017`-tax.full$`2016`)/tax.full$`2016`*100
pct_2018<-tax.pct[,3]<-(tax.full$`2018`-tax.full$`2017`)/tax.full$`2017`*100
tax.pct<-data.frame(Municipalities,pct_2017,pct_2018)
```

>>>>

Municipalities<-tax.full$Municipalities
pct_2017<-(tax.full$`2017`-tax.full$`2016`)/tax.full$`2016`*100
pct_2018<-tax.pct[,3]<-(tax.full$`2018`-tax.full$`2017`)/tax.full$`2017`*100
tax.pct<-data.frame(Municipalities,pct_2017,pct_2018)

write.csv(tax.full, here("data","tax_final.csv"))
write.csv(tax.pct, here("data","tax_pct.csv"))
```
